A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation

### 2020-04-14 alpibot.tex
Adjustments on the abstract.

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Patients that suffer Chronic Obstructive Pulmonary Disease (COPD) underwent a procedure called Pulmonary Rehabilitation that helps them to improve disease prognosis.  During Pulmonary Rehabilitation procedures patients require external oxygen assistance.  The oxygen tank cannot be carried by the patient and some external assistance is required.   In this work a basic robot follower is proposed to carry the oxygen tank based on a differential tethered scheme.  Two algorithms are proposed in a very basic configuration.  
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Patients that suffer Chronic Obstructive Pulmonary Disease (COPD) underwent a procedure called Pulmonary Rehabilitation that helps them to improve disease prognosis.  During Pulmonary Rehabilitation procedures patients require external oxygen assistance.  The oxygen tank cannot be carried by the patient and external assistance is required.   This work provides an initial study on the controlling mechanism of a differential tethered robot that implements a leader-follower configuration to carry the oxygen tank for Pulmonary Rehabilitation procedures.  Two alternative control strategies are proposed.  Results are simulated and tested on a real prototype in a Motion Capture System.
\end{abstract}
